\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-12 paper.qmd
Add descriptions according to b2 computation

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > 2 \times s_1$ and $a_1 > \frac{1-s_1}{b_1 -1}$. The minimum $a_1$ that satisfies the constraints will be selected. For regular hexagons, $a_2 = \frac{2}{\sqrt(3)}a_1$. Therefore, $a_2$ is computed for the minimum $a_1$. According to the upper bound of the NLDR, $b_2 = \left\lceil\frac{r_2 - s_2}{v_2} + 1\right\rceil$, where $v_2 = \frac{a_2}{2} + \sqrt{{(\frac{a_2}{2})}^2 - {(\frac{a_1}{2})}^2}$.

@@

<!-- PaCMAP layout with author's suggested parameter choice-->
```{r}
#| warning: false
#| echo: false

## Import data
training_data_mnist <- read_rds("data/mnist/mnist_10_pcs_of_digit_1.rds")
training_data_mnist <- training_data_mnist |>
  mutate(ID = 1:NROW(training_data_mnist))

@@

<!--Render the images in different selected location in 2D layout-->
```{r}
#| warning: false
#| echo: false

## Data with pixel values
mnist_data <- read_rds("data/mnist/mnist_digit_1.rds")

@@

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| echo: false
#| fig-cap: "(a) 2D layout from PaCMAP applied for the digit 1 of the MNIST dataset. Is this a best representation of the original data?, and (b) Images of the handwritten digit 1. The angle of the digit 1 varies along non-linear structure."
#| label: fig-pacmapauthor
#| fig-pos: H

@@

>>>>

The value for $b_2$ is computed by fixing $b_1$. Considering the lower bound of the NLDR, $a_1 > 2 \times s_1$, and $a_1 > \frac{1-s_1}{b_1 -1}$. Similarly, according to the upper bound of the NLDR, $a_1 > \frac{2(r_2 - s_2)}{\sqrt{3}(b_2 - 1)}$, because $a_2 = \frac{\sqrt(3)}{2}a_1$ for regular hexagons. The $a_1$ that satisfies the constraints will be selected. Therefore, $b_2 = \Big\lceil1 +\frac{2(r_2 - s_2)(b_1 - 1)}{\sqrt{3}(1-s_1)}\Big\rceil$.

@@

<!-- PaCMAP layout with author's suggested parameter choice-->
```{r}
## Import data
training_data_mnist <- read_rds("data/mnist/mnist_10_pcs_of_digit_1.rds")
training_data_mnist <- training_data_mnist |>
  mutate(ID = 1:NROW(training_data_mnist))

@@

<!--Render the images in different selected location in 2D layout-->
```{r}
## Data with pixel values
mnist_data <- read_rds("data/mnist/mnist_digit_1.rds")

@@

<!--PaCMAP param: n_components=2, n_neighbors=10, init=random, MN_ratio=0.9, FP_ratio=2.0-->
```{r}
#| fig-cap: "(a) 2D layout from PaCMAP applied for the digit 1 of the MNIST dataset. Is this a best representation of the original data?, and (b) Images of the handwritten digit 1. The angle of the digit 1 varies along non-linear structure."
#| label: fig-pacmapauthor
#| fig-pos: H

@@

<!-- Fit the model and compute error-->
```{r}

```

<!--images that occur large error-->
<!-- within the nonlinear structure-->
```{r}
pixels_gathered <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  tidyr::extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% c( 4699, 4785, 5173, 6671, 2186, 4636, 4882, 
                          773, 2825, 6169, 6948, 5987, 1282, 7715, 
                          622, 2989, 6912, 4370, 1227, 4042, 2444, 
                          836, 1654))

imge_error_sample_within <- pixels_gathered |> 
  ggplot(aes(x, y, fill = value)) +  
  geom_tile() +  
  facet_wrap(~ factor(instance, levels = c( 4699, 4785, 5173, 6671, 2186, 4636, 
                                            4882, 773, 2825, 6169, 6948, 5987, 
                                            1282, 7715, 622, 2989, 6912, 4370, 
                                            1227, 4042, 2444, 836, 1654)), 
             ncol = 12) +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())
```

<!--outside the nonlinear structure-->
```{r}
#| eval: false

img_error <- error_df |> 
  filter(total >= 8) |> 
  filter((!ID %in% c(4699, 4785, 5173, 6671, 2186, 4636, 4882, 773, 
                            2825, 6169, 6948, 5987, 1282, 7715, 622, 2989, 
                            6912, 4370, 1227, 4042, 2444, 836, 1654))) |>
  pull(ID)

pixels_gathered <-  mnist_data |>
  mutate(instance = row_number()) |>
  gather(pixel, value, -Label, -instance) |>
  extract(pixel, "pixel", "(\\d+)", convert = TRUE) |>
  mutate(pixel = pixel - 2, x = pixel %% 28, y = 28 - pixel %/% 28) |>
  filter(instance %in% img_error)

imge_error_sample <- pixels_gathered |> 
  ggplot(aes(x, y, fill = value)) +  
  geom_tile() +  
  facet_wrap(~ instance, ncol = 11) +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())
```

```{r}
#| eval: false
##| echo: false
#| fig-cap: "(a) Images of handwritten digit 1 which occur large model error within the nonlinear strcuture, and (b) Images of handwritten digit 1 which occur large model error outside the nonlinear structure."
#| label: fig-anomalies
#| out-width: 100%
#| fig-pos: H

imge_error_sample_within + imge_error_sample +
  plot_annotation(tag_levels = 'a')
```

### 2024-05-12 paper.tex
Add descriptions according to b2 computation

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > 2 \times s_1\) and
\(a_1 > \frac{1-s_1}{b_1 -1}\). The minimum \(a_1\) that satisfies the
constraints will be selected. For regular hexagons,
\(a_2 = \frac{2}{\sqrt(3)}a_1\). Therefore, \(a_2\) is computed for the
minimum \(a_1\). According to the upper bound of the NLDR,
\(b_2 = \left\lceil\frac{r_2 - s_2}{v_2} + 1\right\rceil\), where
\(v_2 = \frac{a_2}{2} + \sqrt{{(\frac{a_2}{2})}^2 - {(\frac{a_1}{2})}^2}\).

>>>>

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > 2 \times s_1\), and
\(a_1 > \frac{1-s_1}{b_1 -1}\). Similarly, according to the upper bound
of the NLDR, \(a_1 > \frac{2(r_2 - s_2)}{\sqrt{3}(b_2 - 1)}\), because
\(a_2 = \frac{\sqrt(3)}{2}a_1\) for regular hexagons. The \(a_1\) that
satisfies the constraints will be selected. Therefore,
\(b_2 = \Big\lceil1 +\frac{2(r_2 - s_2)(b_1 - 1)}{\sqrt{3}(1-s_1)}\Big\rceil\).
